MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
struggling with the graph(home win loss)

df$BLANK<-"" #for some reason cast function does not work with last column in dataframe, so I have created this BLANK column as I need to use AWAY_TEAM colum (it was a last column). 
```

@@

table(aa$WINNER) [2]
#home wins:
hh<-sum(aa$WINNER=="HOME")
#Away wins:
aw<-sum(aa$WINNER=="AWAY")
#percentage of home team winning: 
round(hh/(hh+aw),2)
```

@@

aa2<- cast(aa, AWAY_TEAM ~ WINNER); names(aa2)[1]<-"TEAM"
aa2$WIN_PCT_AWAY<-round(aa2$HOME/(aa2$HOME+aa2$AWAY),2)

@@

ggplot(aa3,aes(x=TEAM, y= WIN_PCT_HOME, col= HOME_ADV))+ geom_point()
#TO BE UPDATED
```

>>>>

df$BLANK<-"" #for some reason cast function does not work with last column in dataframe, so I have created this BLANK column as I need to use AWAY_TEAM colum (it was a last column).

write.csv(df,"shot_logs1010.csv")
```

@@

table(aa$WINNER)
#home wins:
hh<-sum(aa$WINNER=="HOME")
#Away wins:
aw<-sum(aa$WINNER=="AWAY")
#percentage of home team winning: 
round(hh/(hh+aw),2)
```

@@

aa2<- cast(aa, AWAY_TEAM ~ WINNER); names(aa2)[1]<-"TEAM"
aa2$WIN_PCT_AWAY<-round(aa2$AWAY/(aa2$HOME+aa2$AWAY),2)

@@

#aa3$WIN_PCT_HOME <- with(aa3, reorder(WIN_PCT_HOME, WIN_PCT_HOME, function(aa3) - length(aa3)))
#ggplot(aa3) + geom_point(aes(WIN_PCT_HOME))

aa3<-aa3[order(aa3$WIN_PCT_HOME,decreasing=TRUE),]
head(aa3)

#home_pct <- table(aa3$WIN_PCT_HOME)
#home_pct_level <- names(home_pct)[order(home_pct)]
#aa3$WIN_PCT_HOME2 <- factor(aa3$WIN_PCT_HOME, levels = home_pct_level)
head(aa3)

ggplot(aa3,aes(x=TEAM,y= WIN_PCT_HOME,colour = "HOME")) +geom_point() + geom_point(aes(y= WIN_PCT_AWAY, colour ="AWAY"))

#ggplot(aa3,aes(x=TEAM))+ geom_point(aes(y= WIN_PCT_HOME,colour = "HOME")) + geom_point(aes(y= WIN_PCT_AWAY, colour ="AWAY"))
#TO BE UPDATED
```
